Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-08-22 doc/RMD/mlg-mcg.Rmd
update mlg-mcg to save the heterothallic pairings

```{r community_counting, fig.width = 6, fig.height = 3.5}
in_reach <- ego(g, 2, nodes = which(grepl("Genotype", V(g)$type)), mode = "all") %>%
  map_df(function(.x) as_tibble(list(MLG = list(names(.x[grepl("MLG", names(.x))])), 
                                     MCG = list(names(.x[!grepl("MLG", names(.x))])), 
                                     WHO = names(.x[1])
                                     )
                                )) %>% 
  mutate(N = lengths(MLG))

in_reach_summary <- in_reach %>% 
  group_by(N) %>%
  summarize(E = diversity_stats(as.integer(table(unlist(MCG))))["E.5"], 
            MCG = n_distinct(unlist(MCG)), 
            MLG = n())
knitr::kable(in_reach_summary)
ggplot(in_reach_summary, aes(x = N - 1, y = MLG, fill = E)) +
  geom_segment(aes(yend = 0, xend = N-1)) +
  geom_point(aes(size = MCG), pch = 21) +
  # ggrepel::geom_label_repel(aes(label = MCG)) +
  viridis::scale_fill_viridis(option = "D") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/1.75) +
  theme(axis.text = element_text(color = "black")) +
  scale_y_continuous(expand = c(0, 0.1), limits = c(0, 25)) +
  scale_x_continuous(expand = c(0, 0.1), breaks = c((0:6)*10), limits = c(-2, 60)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50", linetype = 3)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank()) +
  labs(list(fill = expression(E[5]), 
            size = "MCG"
            # caption = "size and fill represent\nthe number and distribution\nof MCG"
            )) +
  xlab("Maximum Heterothallic Pairings") +
  ylab("Multilocus Genotypes")
```

>>>>

```{r community_counting, fig.width = 6, fig.height = 3.5}
in_reach <- ego(g, 2, nodes = which(grepl("Genotype", V(g)$type)), mode = "all") %>%
  map_df(function(.x){
    as_tibble(
      list(
        MLG = list(names(.x[grepl("MLG", names(.x))][-1])), # -1 to remove self
        MCG = list(names(.x[!grepl("MLG", names(.x))])), 
        WHO = names(.x[1])
        )
      )
    }) %>% 
  mutate(N = lengths(MLG))

in_reach_summary <- in_reach %>% 
  group_by(N) %>%
  summarize(E = diversity_stats(as.integer(table(unlist(MCG))))["E.5"], 
            MCG = n_distinct(unlist(MCG)), 
            MLG = n())
knitr::kable(in_reach_summary)
in_reach_plot <- ggplot(in_reach_summary, aes(x = N, y = MLG, fill = E)) +
  geom_segment(aes(yend = 0, xend = N)) +
  geom_point(aes(size = MCG), pch = 21) +
  # ggrepel::geom_label_repel(aes(label = MCG)) +
  viridis::scale_fill_viridis(option = "D") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/1.75) +
  theme(axis.text = element_text(color = "black")) +
  scale_y_continuous(expand = c(0, 0.1), limits = c(0, 25)) +
  scale_x_continuous(expand = c(0, 0.1), breaks = c((0:6)*10), limits = c(-2, 60)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50", linetype = 3)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank()) +
  labs(list(fill = expression(E[5]), 
            size = "MCG"
            # caption = "size and fill represent\nthe number and distribution\nof MCG"
            )) +
  xlab("Potential Heterothallic Pairings") +
  ylab("Multilocus Genotypes")
in_reach_plot
if (!interactive()){
  save(in_reach, in_reach_summary, in_reach_plot, file = file.path(PROJHOME, "data/heterothallic-pairings.rda"))
}
```
